Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
dhrystone 2.0
take care of last XXX

In the example of the \texttt{malloc} operation, replaced by a call to GC
code, this GC code can invoke a complete collection of dead objects, and
can thus be arbitrarily complicated.  Still, our GC code is entirely
written in plain Python, and it manipulates "objects" that are still at
a lower level: pointer and address objects.  Even with the restriction
of having to use pointer-like and address-like objects, Python remains
more expressive than, say, C to write a GC.  [XXX see also Jikes]

@@

The tool-chain has been tested with and can sucessfully apply
transformations enabling various combinations of features. The
translated interpreters are benchmarked using pystone (a [Dhrystone]
derivative traditionally used by the Python community, although it is
a rather poor benchmark) and the classical [Richards] benchmark and
compared against [CPython] 2.4.3 results and are summarized in table
\ref{perfsumm}.

>>>>

In the example of the \texttt{malloc} operation, replaced by a call to
GC code, this GC code can invoke a complete collection of dead
objects, and can thus be arbitrarily complicated.  Still, our GC code
is entirely written in plain Python, and it manipulates "objects" that
are still at a lower level: pointer and address objects.  Even with
the restriction of having to use pointer-like and address-like
objects, Python remains more expressive than, say, C to write a GC
(Jikes RVM's GC work \cite{JikesGC} was the inspiration to try to
express GCs in Python, see \ref{relatedwork}).

@@

The tool-chain has been tested with and can sucessfully apply
transformations enabling various combinations of features. The
translated interpreters are benchmarked using pystone (a [Dhrystone] 2.0
derivative traditionally used by the Python community, although it is
a rather poor benchmark) and the classical [Richards] benchmark and
compared against [CPython] 2.4.3 results and are summarized in table
\ref{perfsumm}.
